---
title: "A-quick-tour-of-mixHMMR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-mixHMMR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(mixHMMR)
```

# Introduction

**mixHMMR** is a contributed R package for clustering and segmentation. It provides functions for parameter estimation via the EM algorithm. This document gives a quick tour of **mixHMMR** (version `r packageVersion("mixHMMR")`) functionalities. It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr) package for production. 
See `help(package="mixHMMR")` for further details and references provided by `citation("mixHMMR")`.

# Load data

```{r}
data("simulatedtimeseries")
fData <- FData(simulatedtimeseries$X, t(simulatedtimeseries[, 2:ncol(simulatedtimeseries)]))
```

# Set up mixHMMR model parameters

```{r}
K <- 3 # number of clusters
R <- 3 # number of regimes/states
p <- 2 # degree of the polynomial regression
variance_type = variance_types$heteroskedastic
modelMixHMMR <- ModelMixHMMR(fData, K, R, p, variance_type)
```

# Set up EM parameters

```{r}
ordered_states = TRUE
n_tries = 1
max_iter = 1000
init_kmeans = TRUE
threshold = 1e-6
verbose = TRUE
```

# Estimation

```{r}
solution <- EM(modelMixHMMR, ordered_states, n_tries, max_iter, init_kmeans, threshold, verbose)
```

# Plots

```{r}
solution$plot()
```
